### 2021-11-13 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@c8118ede5a7a84925c6213b30f3a8c47fb6759e7 🚀

Within the last several hundred years, human activity has rapidly
reshaped both Earth's surface. These changes can roughly be divided into
two categories: (1) Land-use change, which has rapidly reshaped our
planet's surface and restructured habitats for every species, and (2)
climate change, words here, as a result of greenhouse gas emissions. As
a result \emph{ecological forecasting} (\textbf{dietze?}), or modeling
how ecological systems will change over time, has as an imperative to
mitigate the effect of these changes on Earth's ecosystems, their
functioning, and the services they provide to humans.

@@

In recent years, there has been an interest in an epistemological shift
in ecology. emerged to explain particular phenomena at particular
scales.

To shift ecology into a predictive science. The justification for this
shift is twofold: (1) bogged down philosophy of science, by further
rooting our understanding of ecosystem function and dynamics in an
ability to predict their structure (\textbf{PredictiveEcology?}). and
(2) the practical need for models for \emph{ecological forecasting}.

>>>>

Within the last several hundred years, human activity has rapidly
reshaped Earth's surface. These changes can roughly be divided into two
categories: (1) Land-use change, where Earth's surface changes and (2)
climate change, words here, as a result of greenhouse gas emissions.

As a result \emph{ecological forecasting} (\textbf{dietze?}), or
modeling how ecological systems will change over time, has as an
imperative to mitigate the effect of these changes on Earth's
ecosystems, their functioning, and the services they provide to humans.

@@

emerged to explain particular phenomena at particular scales.

In recent years, there has been an interest in an epistemological shift
in ecology. To shift ecology into a predictive science. The
justification for this shift is twofold: (1) bogged down philosophy of
science, by further rooting our understanding of ecosystem function and
dynamics in an ability to predict their structure
(\textbf{PredictiveEcology?}). and (2) the practical need for models for
\emph{ecological forecasting}.
